---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ukgeoportal

<!-- badges: start -->
<!-- badges: end -->

The goal of ukgeoportal is to provide easy access to the UK's [Geoportal](https://geoportal.statistics.gov.uk/).

```{r, echo=FALSE, eval=FALSE}
# The following commands were used to create this package
usethis::use_description()
usethis::use_agpl_license()
usethis::use_r()

```

Because ESRI [doesn't publish OpenAPI compliant .yml files](https://github.com/Esri/geoportal-server/issues/297) describing their APIs, this package  doesn't use the wonderful [`{beekeeper}`](https://beekeeper.api2r.org/) package to generate the API wrappers.

Instead it uses `sf` to make the API calls.

The aim is to be as minimal and easy-to-maintain as possible.

The history of attempts to gain programmatic access to the Geoportal suggests that ease-of-updates and minimalism are key to success.

## Installation

```{r, eval=FALSE}
remotes::install_github("robinlovelace/ukgeoportal")
```